Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
update

We note that the \note{store? update function? can a store be monotonic?} is monotonic; it continuously grows and never shrinks. This property
guarantees that in analyzing the \note{update function? store? pick the right word}, a fixed point can always be reached.

@@

The codomain of all binding stores @Storable@ is the same
as previously defined for CESK machines.
The codomain of continuation stores @Cont@, on the other hand, is comprised of
a @Frame@ object and a continuation address @KAddr@.
To mimic the runtime call stack, @KAddr@ plays the role of
representing the remaining stack frames.
\todo{talk about nondet of cont deref?}

@@

If we instantiate $k$ to be $0$, the history degenerates to an empty list,
and we obtain a monovariant analysis (i.e., it does
not differentiate values at different call sites). In this case, the address
space collapses to the space of variable names.
Note that regarding the ambiguity in $k$-CFA\cite{Gilray:2016:ACP:2951913.2951936},
the code here actually implements call+return \note{call+return, call/return, etc.? Check this} sensitivity.

@@

However, in contrast to the concrete CESK machine, the
@drive@ function performs collecting semantics instead of the valuation
semantics. That is, for the purpose of analyzing programs, the function @drive@
collects all the intermediate machine states as the program is abstractly executing.
The following code shows a variant of the worklist algorithm to find the fixed-point
of the set of states.\note{JD: I changed all of this to worklist instead of work list in favor of the worklist algorithm. Change this back if it's wrong.}
Function @drive@ always applies function @step@ to the head element @hd@ of
the worklist @todo@ if @hd@ is unseen. It then inserts the result of @step@ to
the rest of worklist, and in the meantime adds @hd@ to the explored states set.
If the worklist is empty, @drive@ simply returns the set of reachable states
up to the current execution point.

>>>>

We note that both the value store and continuation store are monotonic; 
it continuously grows and never shrinks. This property guarantees that 
a fixed point of store can always be reached through Kleene's 
iteration when analyzing the program

@@

The codomain of binding stores @Storable@ is the same as previously defined for CESK machines.
The codomain of continuation stores @Cont@, on the other hand, is comprised of
a @Frame@ object and a continuation address @KAddr@.
To mimic the runtime call stack, @KAddr@ plays the role of
representing the remaining stack frames. 
But since the continuation store may contain multiple continuations,
the dereferencing of continuation addresses is also nondeterministic.

@@

If we instantiate $k$ to be $0$, the history degenerates to an empty list,
and we obtain a monovariant analysis (i.e., it does
not differentiate values at different call sites). In this case, the address
space collapses to the space of variable names.
Note that regarding the ambiguity in $k$-CFA\cite{Gilray:2016:ACP:2951913.2951936},
the code here actually implements call+return sensitivity.

@@

However, in contrast to the concrete CESK machine, the
@drive@ function performs collecting semantics instead of the valuation
semantics. That is, for the purpose of analyzing programs, the function @drive@
collects all the intermediate machine states as the program is abstractly executing.
The following code shows a variant of the worklist algorithm to find the fixed-point
of the set of states.
Function @drive@ always applies function @step@ to the head element @hd@ of
the worklist @todo@ if @hd@ is unseen. It then inserts the result of @step@ to
the rest of worklist, and in the meantime adds @hd@ to the explored states set.
If the worklist is empty, @drive@ simply returns the set of reachable states
up to the current execution point.
